---
title: "Homework4"
format: html
editor: visual
---
## Calling Libraries

```{r}
library(tidyverse)
library(lubridate)
library(dplyr)
library(readxl)
library(readr)
```


### Task1: Conceptual Questions

1) The relative path would be ../mydata.csv

2) One of the major benefits of using R projects is the ability to keep multiple analysis separate.

3)Git is a version control software and Github in the online hosting service for Git-based projects

4) 
iris |>
 order(iris$species) |>
  subset(iris$petal.length <1.55) |>
   grep("^Petal",names(iris)) 


### Task 2: Reading Delimited Data

### Glass Data 

```{r}
glass<- read_delim("https://www4.stat.ncsu.edu/~online/datasets/glass.data",
                   delim=",",
                   col_names = c("ID","RI","Na","Mg","Al","Si","K","Ca","Ba","Fe","typ"))
glass|> mutate(typ2=ifelse(glass$typ==1,"Building_Windows_float_processed",
                ifelse(glass$typ==2,"Building_Windows_non_Float_Processed",
                       
                       
                               ifelse(glass$typ==3,"Vehicle_Windows_Float_Processed",
                                      ifelse(glass$typ==4,"Vehicle_Windows_Non_Float_Processed",
                                             ifelse(glass$typ==5,"Containers",
                                                    ifelse(glass$typ==6,"Tableware",
                                                           ifelse(glass$typ==7,"Headlamps","Other"))))   )
                           ) ) ) |>
  
               filter(Fe <0.2 & (typ2=='Tableware' | typ2=='Headlamps'))

#Calling the tibble
glass

```

### Yeast Data

```{r}
library(readr)
yeast<-read_table("https://www4.stat.ncsu.edu/online/datasets/yeast.data", col_names=c("seq_name","mcg","gvh","alm","mit","erl","pox","vac","nuc","class")
)
#Calling the tibble
yeast

#Creating a Chain
yeast |>
  select(2:7,10) |>
    group_by(class) |>
  mutate(across(where(is.numeric),list(mean=mean, median=median), .names = "{.col}_{.fn}"))

```

## Task 3: Combining Excel and Delimited Data

```{r}
#Reading in White Wine 1st sheet
wwine<-read_excel("white-wine.xlsx",
                sheet=excel_sheets("white-wine.xlsx")[1]  )
wwine

#Reading in Names
wnames<-read_excel("white-wine.xlsx",
                sheet=excel_sheets("white-wine.xlsx")[2]  )

#Transposing the Names
wnames2<-data.frame(t(sapply(wnames,c)))

#Renaming
colnames(wwine)<-wnames2

wwine<-data_frame(wwine,type='White')



```

```{r}
#Reading in Red wine 
rwine<-read_delim("https://www4.stat.ncsu.edu/~online/datasets/red-wine.csv",delim=";")

rwine<-data_frame(rwine,type='Red')


```

```{r}
#Combining Data Sets
allwine<-bind_rows(rwine,wwine)

allwine$alcohol<-as.numeric(allwine$alcohol)

allwine |>
  filter(quality >6.5) |>
   arrange(desc(quality)) |>
    select(`citric acid`,alcohol,type,quality) |>
     group_by(quality)|>
 mutate(mean=mean(allwine$alcohol),
        sd=sd(allwine$alcohol))


    
```

